\section{Changes to the code}
\begin{itemize}
    \item Changed servers and clients to read config files properly using
        ClassLoader instead of an absolute path.
    \item Changed HTTP Proxy slaveAddress sets to lists instead, to be able to
        use \texttt{.get(idx)}
    \item Implemented a simple round-robin based load balancing using a volatile
        incremented variable, which defers to the master server after enough
        tries resulting in time-outs. The strategy also ensures that non-timeout
        related exceptions propagate immediately and cause failure.
    \item Changed SlaveCertainBookStore to implement ReplicatedStockManager and
        ReplicatedBookStore instead of the read-only variants.
    \item Added handling of update requests to slaves, through the same book
        tags as the master server uses, and implementation through the standard
        methods offered by ReplicatedStockManager and ReplicatedBookStore.
    \item Added a new string constant to BookStoreClientConstants to represent
        failure to issue a read-request to the cluster, which triggers after a
        threshhold of tries is exhausted.
    \item Implemented concurrent handling of proxy requests by giving each HTTP
        Proxy a HttpClient, which is passed to the Callable that performs the
        actual query. The BookStoreUtility.SendAndRecv will block on the
        ContentExchange, while other requests get fulfilled by the HttpClient.
    \item TODO: Authenticate that a write-related request is really coming from
        the Master server.
    \item TODO: Testing.
\end{itemize}
